---
title: "COP21 Datapack App analytics"
output:
  pdf_document: default
html_document:
  df_print: paged
lang: "en-US"
date: '`r format(Sys.time(), "%d %B, %Y %H:%M")`'
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(data.table)
require(magrittr)
require(purrr)
require(dplyr)
require(tidyr)
require(knitr)
require(ggplot2)
require(paws)

Sys.setlocale("LC_MESSAGES", 'en_GB.UTF-8')
Sys.setenv(LANG = "en_US.UTF-8")

s3<-paws::s3()
s3_files <- s3$list_objects_v2(Bucket=Sys.getenv("AWS_S3_BUCKET"),Prefix="app_analytics/cop21/") 
files_on_s3<-s3_files$Contents %>% map(.,function(x) x$Key) %>% unlist()

tmpdir<-tempdir()
dir.create(paste0(tmpdir,"/","app_analytics"))
dir.create(paste0(tmpdir,"/","app_analytics/cop21"))

  for ( i in 1:length(files_on_s3) ) {
  print(paste("Getting",files_on_s3[i]))
  s3_download<-s3$get_object( Bucket=Sys.getenv("AWS_S3_BUCKET"),
                 Key = files_on_s3[i])
  s3_download_body <- s3_download$Body
  # Write output to file
file_name2 <- paste0(tmpdir,"/",files_on_s3[i])
writeBin(s3_download_body, con = file_name2)

}


read_plus <- function(flnm) {
  fread(flnm) %>% 
    mutate(filename = flnm)
}

file_prefix<-paste0(tmpdir,"/app_analytics/cop21/")
d <- list.files(path = file_prefix,pattern = "*.csv",full.names = TRUE) %>% 
  map_df(~read_plus(.)) %>% 
  dplyr::mutate(`filename` = stringr::str_replace(filename,file_prefix,"")) %>% 
  tidyr::separate(`filename`,into=c("sanename","date","time"),sep="_") %>% 
  mutate(time=stringr::str_remove(time,"\\.csv$")) %>% 
  mutate(timestamp = lubridate::parse_date_time(paste(date,time),"ymd HMS")) %>% 
  dplyr::select(-date,-time)
```


## Summary info
```{r echo=FALSE}

total_validations<-d %>% 
  dplyr::select(country_name,timestamp) %>% 
  dplyr::distinct() %>% 
  NROW()
start_date<-as.Date(min(d$timestamp))
end_date<-as.Date(max(d$timestamp))
```


- Total validations: `r total_validations`
- First validation on: `r start_date`
- Last validation on: `r end_date`

## Validations by country


```{r eval=TRUE, echo=FALSE}
validations_by_country_total<-
d %>% 
  dplyr::select(Country=country_name,timestamp) %>% 
  dplyr::distinct() %>% 
  dplyr::group_by(Country) %>% 
  dplyr::summarise(Validations=n()) %>% 
  dplyr::arrange(-Validations)

kable(validations_by_country_total)
```

## Validations by day

```{r eval=TRUE, echo=FALSE}

#Validations by date
validations_by_date_total<-
d %>% 
  dplyr::select(country_name,timestamp) %>% 
  dplyr::distinct() %>% 
  dplyr::mutate(Date=as.Date(timestamp)) %>% 
  dplyr::select(Date) %>% 
  dplyr::group_by(Date) %>% 
  dplyr::summarise(Validations = dplyr::n())

ggplot(validations_by_date_total,aes(x = Date, y= Validations)) + geom_col()


```


## Validation issues

```{r eval=TRUE, echo=FALSE}
#Issue summary

issue_summary<-d %>% dplyr::select(country_name,timestamp,validation_issue_category) %>% 
  dplyr::distinct() %>%
  dplyr::group_by(validation_issue_category) %>% 
  dplyr::summarise(count=dplyr::n()) %>% 
  dplyr::arrange(-count) %>% 
  dplyr::mutate(occurrence_rate = ( (100*count/total_validations) %>% round(.,digits = 1)  ) ) %>% 
  dplyr::select(-count) %>% 
  dplyr::rename(Category = validation_issue_category,
                "Occurrence (%)" = occurrence_rate)


kable(issue_summary)
``` 


```{r eval=TRUE, echo=FALSE}
require(connectapi)
require(lubridate)

days_back <- as.numeric(Sys.getenv("DAYSBACK", 30))

default_content_title <- "Unknown (Deleted Content?)"

report_from <- lubridate::today() - lubridate::ddays(days_back)

client <- connectapi::connect()
shiny <- get_usage_shiny(
  client,
  from = report_from,
  limit = Inf
) %>%
  mutate(
    started = lubridate::ymd_hms(started),
    ended = lubridate::ymd_hms(ended),
    session_duration = ended - started
    ) %>%
  filter(session_duration > lubridate::dseconds(5))

content <- get_usage_static(
  client,
  from = report_from,
  limit = Inf
)

all_users <- get_users(client, page_size = 500)

data <-   list(shiny = shiny, content = content)
```


## Connect server stats
```{r shiny_over_time, eval=TRUE, echo=FALSE}
data$shiny %>%
    mutate(day = round_date(started, "day")) %>% 
    group_by(day) %>% 
    filter(day > today() - ddays(days_back)) %>% 
    summarise(visits = n()) %>% 
    arrange(desc(visits)) %>% 
    {ggplot(., aes(day, visits)) + 
            geom_bar(stat = "identity") + 
            labs(
                y = "# of Shiny Sessions",
                x = NULL
            )}
```


## Datapack sessions by day
```{r datapack_over_time, eval=TRUE, echo=FALSE}
data$shiny %>% 
      mutate(time = ymd_hms(started),
          day = round_date(started, "day")) %>% 
  dplyr::select(content_guid,time,day) %>% 
  group_by(content_guid,day) %>% 
  summarize(visits = n()) %>% 
  arrange(content_guid,desc(visits)) %>% 
  mutate(name = purrr::map_chr(content_guid, ~ content_title(client, .x, default_content_title))) %>% 
  dplyr::filter(name == "Datapack") %>% 
  {  ggplot(., aes(day, visits)) + 
     geom_bar(stat = "identity") +  
     labs(
       y = "# of Datapack sessions by day",
       x = "Date"
     )} 